A decomposition based on constrained clustering algorithms for JSP\thanks{Supported by organization x.}

### 2021-10-01 Artificial Intelligence and Machine Learning/PADL_conference/Paper_draft_v1.tex
abstract

\begin{document}
%
\title{A decomposition based on constrained clustering algorithms for JSP\thanks{Supported by organization x.}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Mohammed M. S. El-Kholany\inst{1}\orcidID{0000-0002-1088-2081} \and
Konstantin Schekotihin\inst{1}\orcidID{0000-0002-0286-0958} \and
Martin Gebser\inst{1,2}\orcidID{0000--0000-0000-0000}}
%
\authorrunning{M. El-Kholany et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Alpen-Adria-Universität Klagenfurt, Klagenfurt, Austria 
\email{\{mohammed.el-kholany, konstantin.schekotihin and martin.gebser\}@aau.at}\\
%\url{http://www.springer.com/gp/computer-science/lncs} \and
Technische Universität Graz, Graz, Austria\\
\email{mgebser@ist.tugraz.at}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Scheduling decision in production planning plays a significant role in the manufacturing industry. A good schedule may lead to solve production problems and improve productivity. Job-shop Scheduling Problem (JSP) is one of the most crucial problems in production systems. JSP deals with allocating tasks on resources and determining the sequence of the operations on each machine while completing all tasks as early as possible. One of the most effective approaches studied by many researchers for solving the JSP is decomposition. This work investigates applying the decomposition strategy to split the problem into a series of sub-problems using data mining methodologies. This study proposes a constrained clustering algorithm to group the data objects (operations) into clusters, where each cluster is a Time Window (TW). The decomposition process depends on two main phases; the first phase is to extract features to predict the sequence of the operations on each machine. These features are extracted either from the problem itself or from solutions obtained by other heuristics. The second phase is to develop a constrained clustering algorithm to assign each data object (an operation) into a cluster. We solved the problem using the Answer Set Programming model, and tested our proposed algorithm on a set of benchmark instances, and the results showed that our proposed outperformed other heuristics in most cases. The results also showed that some features like \textit{Remaining Processing Time}, \textit{Machine Load} and \textit{Earliest Starting Time} have a significant impact on the solution quality.

@@

\subsection{\textit{Operation}}
The \textit{Operation} attribute is an ordinal value to represent the rank of each operation in its job.

>>>>

\begin{document}
%
\title{A decomposition based on constrained clustering algorithms for JSP\thanks{Supported by organization x.}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Mohammed M. S. El-Kholany\inst{1}\orcidID{0000-0002-1088-2081} \and
Konstantin Schekotihin\inst{1}\orcidID{0000-0002-0286-0958} \and
Martin Gebser\inst{1,2}\orcidID{0000--0000-0000-0000}}
%
\authorrunning{M. El-Kholany et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Alpen-Adria-Universität Klagenfurt, Klagenfurt, Austria 
\email{\{mohammed.el-kholany, konstantin.schekotihin and martin.gebser\}@aau.at}\\
%\url{http://www.springer.com/gp/computer-science/lncs} \and
Technische Universität Graz, Graz, Austria\\
\email{mgebser@ist.tugraz.at}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Scheduling is a crucial problem appearing in various domains, such as manufacturing, transportation, or healthcare. In most problem definitions, the goal is to schedule a given set of operations on available resources to complete the operations as early as possible. Unfortunately, most scheduling problems cannot be solved efficiently. Therefore, the research of suitable approximation methods is of primary importance.

This work suggests a novel approximation approach based on problem decomposition with data mining methodologies. This study proposes a constrained clustering algorithm to group the operations into clusters corresponding to time windows in which these operations must be scheduled. 
The decomposition process depends on two main phases. The first phase is to extract features to predict the sequence of the operations on each resource. These features are extracted either from the problem itself or from solutions obtained by other heuristics. The second phase is to develop a constrained clustering algorithm to assign each operation into a time window. We solved the problem using the Answer Set Programming. Evaluation results show that our proposed outperformed other heuristic schedulers in most cases, where features, like \textit{Remaining Processing Time}, \textit{Machine Load}, and \textit{Earliest Starting Time}, contributed significantly to the solution quality.

@@

\subsection{\textit{Operation}}
The \textit{operation} attribute is an ordinal value to represent the rank of each operation in its job.
